A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-19 writeup/paper.tex
Added paragraph to related work that re-states our contributions

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3154 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of the 5,284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%Within MTurk, those who need work completed (`requesters') post individual HITs. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accepted tasks.

%The convenience and low cost of using MTurk has made it popular among researchers. Because of the lack of oversight and the high potential for spam, however, most of the data collected from MTurk has been limited to simple tasks for which inter-annotator agreement is expected to be high (see Related Work section below). We explore the idea that MTurk's machinery is flexible enough to support more complex tasks requiring more nuanced quality control mechanisms, which could allow it to be a competitive alternative to professional data annotations.

%\section{Related Work}

%Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels. Snow et al. describes the success of using redundant non-expert labels to substitute for professional annotations, achieving comparable quality for much lower cost. The tasks from which these conclusions were drawn, however, were kept simple and easily-verifiable, with annotations restricted to either multiple choice or bounded numeric inputs. As NLP research advances, the level of expertise required from annotators advances as well. Callison-Burch et al. report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.

@@

%No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

@@

>>>>

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=7in]{figures/natlang-pie}
\caption{Self-reported native language of 3,154 bilingual turkers}
\label{lang-pie}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

To contrast our research with previous work, the main contributions of this paper are: (1) a robust methodology for assessing the bilingual  skills of anonymous crowdworkers, (2) the largest-scale census to date of language skills of workers on MTurk, and (3) a detailed analysis of the data gathered in our study, including the quality of the translations and recommendations for  languages that are feasible for near-term creation of multi-lingual technologies.
